Verification of a TCP/IP stack

### 2020-09-04 paper/paper.tex
Rework section on SPARK inserted in new top-level section for Specification

@@

\subsection{The SPARK programming language}

    SPARK~\cite{mccormick2015building} is a tool that can be used to formally prove properties on a subset of Ada such that
    information flow, absence of runtime errors and functional correctness. The subset of Ada that can be analyzed by SPARK
    grows constantly and rapidly, recently with the addition of pointers~\cite{dross2020recursive}.
    In Ada, contracts can be attached to subprograms as pre- and postconditions which allows functional and modular analysis.
    The pre- and postconditions are exported to be proved by SMT solvers thanks to the Why3 tool.

>>>>

\section{Specification Techniques Used}

\subsection{The SPARK Programming Language}

Ada is a general-purpose procedural programming language. The design of the Ada
language puts great emphasis on the safety and correctness of the program. This
objective is realized by using a readable syntax that uses keywords instead of
symbols where reasonable. The type system is strong and strict and many
potential violations of type constraints can be detected statically by the
compiler. If not, a run-time check is inserted into the program, to guarantee
the detection of incorrect situations. Ada 2012 introduced contract based
programming to Ada. In particular, it is possible to attach pre- and
postconditions to subprograms\footnote{In Ada, a distinction is made between
  functions that return a value, and procedures, which do
  not. \emph{Subprogram} is the term that designates both.}.  These conditions
can be checked during the execution of the program, just like assertions.

SPARK~\cite{mccormick2015building} is the name of a platform that provides
formal verification for Ada. It uses the user-provided contracts and attempts
to prove that the runtime checks cannot fail and that postconditions are
established by the corresponding subprograms.  As formal verification for the
whole Ada language would be intractable, SPARK is also the name of the subset
of the Ada language that is supported by the SPARK tool called
GNATprove\footnote{\url{http://docs.adacore.com/spark2014-docs/html/ug/}}.
This subset contains almost all features of Ada, though sometimes in a
restricted form.  In particular, expressions should be free from side effects,
and aliasing is forbidden (no two variables should share the same memory
location or overlap in memory), including when using pointers thanks to the use
of an ownership policy~\cite{dross2020recursive}.  This restriction greatly
simplifies the memory model used in the SPARK tool: any program variables can
be reasoned about independently from other variables.

GNATprove performs two kinds of analysis modularly on individual subprograms:
information flow to detect reads of uninitialized data and violations of flow
contracts; deductive verification based on the Why3 platform to generate
verification conditions for SMT solvers via a weakest-precondition calculus to
detect possible runtime errors and violations of functional contracts.

\subsection{Interfacing SPARK and C Code}

describe import of C subprograms/export of SPARK subprograms, and how data
types are mapped, also contracts on imported subprograms

\subsection{Dealing with Pointers}

both at top-level and as fields in structures. explain how it relies on the
ownership model. maybe a little bit on dynamic allocation/deallocation (which
will introduce the section later on memory leaks)

\subsection{Specifying the Frame Condition}

describe how models of sockets are defined and used in contracts, based on
ghost code, delta aggregates and Old attribute

@@
